Prediction of the 2020 Presidential Election

### 2020-11-01 outputs/paper/paper.Rmd
added cell counts.rds to post-strat script
added hispanic to cell_counts

library(tidyverse)
library(tinytex)
library(readr)
library(here)
```

@@

@@

>>>>

library(tidyverse)
library(tinytex)
library(readr)
library(here)
library(patchwork)
```

@@

```{r, echo=FALSE, include=FALSE}
#loading in our 2 cleaned datasets

individual_survey <- readRDS(here::here("inputs/cleaned_data","individual-survey.rds"))
post_strat <- readRDS(here::here("inputs/cleaned_data","post-strat.rds"))

@@

(Figure \@ref(fig:age)) 
```{r age, fig.cap="Difference in Age distribution between both datasets", echo = FALSE, fig.width=8, fig.height=4}

individual_age_dist<- individual_survey %>% 
  group_by(age) %>% 
  summarise(num_records = n()) %>% 
  mutate(percentage = 100 * num_records/sum(num_records),
         total_num = sum(num_records),
         data_source = "Nationscape")

post_strat_age_dist <- post_strat %>% 
  group_by(age) %>% 
  summarise(num_records = n()) %>% 
  mutate(percentage = 100 * num_records/sum(num_records),
         total_num = sum(num_records),
         data_source = "ACS")

individual_age_dist %>% 
  union(post_strat_age_dist) %>% 
  ggplot(aes(x = age, y = percentage)) + 
  geom_col() + 
  facet_grid(~data_source) + 
  theme_economist_white() +
  labs(Title = )
